The Calculus of Linear Constructions

### 2022-01-09 writing/draft6/draft6.tex
draft

We further extend CLC with rules for defining inductive linear types in the style of CIC, forming the Calculus of Inductive Linear Constructions (CILC). Standard Linear Logic connectives such a $\otimes$ and $\oplus$ are definable using this generalized mechanism in a straightforward way. Through examples, we show that CILC facilitates lightweight reasoning about stateful programs and protocol enforcement.

We have formalized all major results in Coq and implemented a prototype in OCaml, both of which are available in the first author's Github repository.

@@

\section{Examples}
We shall write examples in the concrete syntax of our implementation. We deliberately chose to model our concrete syntax after Coq such that it would be easier for readers already familiar with Coq to adapt to our syntax.

>>>>

We further extend CLC with rules for defining inductive linear types in the style of CIC, forming the Calculus of Inductive Linear Constructions (CILC). Standard Linear Logic connectives such a $\otimes$ and $\oplus$ are definable using this generalized mechanism in a straightforward way. Through examples in Section \ref{examples}, we show that CILC facilitates lightweight reasoning about stateful programs, protocol enforcement and in-place update of data structures.

We have formalized all major results in Coq and implemented a prototype in OCaml. Additional examples of applications such as safe array access and quantitative reasoning are included with our implementation.

@@

\section{Examples}\label{examples}
We shall write examples in the concrete syntax of our implementation. We deliberately chose to model our concrete syntax after Coq such that it would be easier for readers already familiar with Coq to adapt to our syntax.
